### 2013-01-20 draft.tex
introduction done

\documentclass[12pt,a4paper,oneside,titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcase} 
\usepackage{tocloft}
\usepackage{lastpage}
\usepackage[left=3.5cm,right=1cm,top=2cm,bottom=1.2cm]{geometry}
\author{Kostenko}
\setcounter{tocdepth}{3}%для глубины страницы содаржения
\renewcommand{\baselinestretch}{1.25}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} % точки в содержании для секций
\bibliographystyle{unsrt}
\begin{document}
{
\thispagestyle{empty}
\newpage
\centering

@@

The vision channel is one of the most informative ones.
Data volume from video stream exceeds by several times volumes from other sensors.
Here lies the pitfall - redundancy of information.
%Иногда бывает достаточно нескольких байт информации
Occasionally just a few bytes of information are enough.
For example, we need only the object of interest, and in addition to this, we have other objects, background and fine detail.
In contrast to human, the machine can not optimally handle this task.
Consequence of this problem is the fact that even an ant can navigate better in the complicated situation than existing robots.

@@

\newpage
\section*{Main body}
\addcontentsline{toc}{section}{Main body}
5 pages

>>>>

\documentclass[12pt,a4paper,oneside,titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcase} 
\usepackage{tocloft}
\usepackage{lastpage}
\usepackage[left=3.5cm,right=1cm,top=2cm,bottom=1.2cm]{geometry}
\author{Kostenko}
\setcounter{tocdepth}{3}%для глубины страницы содаржения
\renewcommand{\baselinestretch}{1.25}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} % точки в содержании для секций
\bibliographystyle{unsrt}
\begin{document}
{
\thispagestyle{empty}
\newpage
\centering

@@

The vision channel is one of the most informative ones.
Data volume from video stream exceeds by several times volumes from other sensors.
Here lies the pitfall - redundancy of information.
Occasionally just a few bytes of information are enough.
For example, we need only the object of interest, and in addition to this, we have other objects, background and fine detail.
In contrast to human, the machine can not optimally handle this task.
Consequence of this problem is the fact that even an ant can navigate better in the complicated situation than existing robots.

@@

Nowadays, paradigm proposed D. Marr \cite{marr} is used in image processing.
Point of this one is to process images in sequence:
\begin{enumerate}
  \item image pre-processing
  \item segmentation
  \item distinguish of the geometric structure
  \item determine the semantics
\end{enumerate}
In other words, processing of low-level should be performed at first, then intermediate-level processing and then high-level processing.

In the general form, motion analysis is comparison of consecutive images of the observed scene.

The rest of this paper is organised as follows:
\begin{description}
  \item[Section 2] \hfill \\
  Identification of key problems of object tracking and formulation of the problem.
  \item[Section 3] \hfill \\
  An algorithm of solving the problems and its implementation. 
  \item[Section 4] \hfill \\
  Summing-up, prospects of our algorithm and we formulate sphere of application our method.
\end{description}

\newpage
\section*{Problem statement}
\addcontentsline{toc}{section}{Problem statement}
2-3 pages

\newpage
\section*{Algorithm}
\addcontentsline{toc}{section}{Algorithm}
2-3 pages
